Viscous Erosion in Porous Media

### 2018-03-12 docs/methods/erosion_methods.tex
small changes to paper

In this section, we describe the boundary integral equations employed
for the fluid equations.  We will start by writing the velocity field in
terms of the standard double-layer potential~\cite{laz1963,poz1992}.
Since the double-layer potential representation is only able to
represent force-free and torque-free velocity fields, Power and
Miranda~\cite{pow-mir1987} completed the BIE formulation by introducing
a Stokeslet and Rotlet.  This methodology was extended by Power for
multiply-connected domains~\cite{pow1993}.  In two-dimensions, a stream
function formulation can be used in which case the biharmonic equation
must be solved, and this can be done using BIEs by using analytic
function theory~\cite{gre-kro-may1996}.

  \cite{Moore2007}
\todo[inline]{Bryan do you want to add a bunch of references to your boundary integral papers here (or somewhere else)?}
In particular, we solve the incompressible Stokes equations
with Dirichlet boundary conditions 
\begin{alignat*}{3}
  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
  \uu &= \ff,  && \xx \in \bd\Omega.
\end{alignat*}
The boundary condition $\ff$ is the prescribed velocity $\UU$ on
$\Gamma$, and it is zero on the grains $\gamma$.  As the viscosity $\mu$
also sets the time scale, we take $\mu=1$.  We start by defining the
double-layer potential
\todo[inline]{Do you think we should flesh out this time-scale stuff more precisely? i.e.~By setting $\mu = 1$ and $C = 1$ (the erosion constant), what exactly is the timescale that defines our dimensionless time.}
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
    \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  The
double-layer potential cannot capture velocity fields corresponding to
rigid body motions~\cite{pow-mir1987}.  The rank deficiency is removed
by complementing the double-layer potential with a Stokeslets and
rotlets centered inside each interior body
\begin{align}
  S[\llambda_\ell,\cc_\ell] = \frac{1}{4\pi} \left(-\log \rho \II + 
    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_\ell
  \quad \text{and} \quad
  R[\xi_\ell,\cc_\ell] = \frac{\rr^\perp}{\rho^2}\xi_\ell, 
  \quad \ell=1,\ldots,M,
  \label{eqn:stokeslet_rotlet}
\end{align}
where  $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
$\ell^{th}$ body, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then,
any solution of the Stokes equations with a Dirichlet boundary condition
$\ff$ can be written in terms of the completed double-layer potential
\begin{align}
  \label{eqn:completed_DLP}
  \uu(\xx) = \DD[\eeta](\xx) + 
    \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
    \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{subequations}
\label{eqn:completed_BIE}
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DD[\eeta](\xx) + 
      \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
      \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx) + \NN_0[\eeta](\xx),
      \quad \xx \in \bd\Omega, 
      \label{eqn:DLP}\\
  \llambda_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \eeta(\yy) \, ds_\yy,
  \quad \ell=1,\ldots,M,
  \label{eqn:stokeslet} \\
  \xi_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \yy^\perp \cdot \eeta(\yy)
  \, ds_\yy, \quad \ell=1,\ldots,M.
  \label{eqn:rotlet}
\end{align}
\end{subequations}
Here,
\begin{align*}
  \NN_0[\eeta](\xx) = \int_{\Gamma} 
    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy
\end{align*}
removes the rank one null space that results from the compatibility
constraint associated with the flux-free requirement of $\ff$.

>>>>

In this section, we describe the boundary integral equations employed
for the fluid equations.  In particular, we solve the incompressible
Stokes equations with Dirichlet boundary conditions 
\begin{alignat*}{3}
  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
  \uu &= \ff,  && \xx \in \bd\Omega.
\end{alignat*}
The boundary condition $\ff$ is the prescribed velocity $\UU$ on
$\Gamma$, and it is zero on the grains $\gamma$.  Since we are
interested in two dimensions, a stream function formulation can be used
by recasting the governing equations as a problem in analytic function
theory~\cite{gre-kro-may1996}.  We instead work with the primitive
variables by writing the velocity in terms of the standard double-layer
potential~\cite{lad1963,poz1992}
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
    \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  The double-layer potential representation is only able to
represent force- and torque-free velocity fields, so we complete the
velocity representation with Stokeslets and
Rotlets~\cite{pow-mir1987,pow1993}.

  \cite{Moore2007}
As the viscosity $\mu$ also sets the time scale, we take $\mu=1$.  We
start by defining the double-layer potential
\todo[inline]{Do you think we should flesh out this time-scale stuff more precisely? i.e.~By setting $\mu = 1$ and $C = 1$ (the erosion constant), what exactly is the timescale that defines our dimensionless time.}
The
double-layer potential cannot capture velocity fields corresponding to
rigid body motions~\cite{pow-mir1987}.  The rank deficiency is removed
by complementing the double-layer potential with a Stokeslets and
rotlets centered inside each interior body
\begin{align}
  S[\llambda_\ell,\cc_\ell] = \frac{1}{4\pi} \left(-\log \rho \II + 
    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_\ell
  \quad \text{and} \quad
  R[\xi_\ell,\cc_\ell] = \frac{\rr^\perp}{\rho^2}\xi_\ell, 
  \quad \ell=1,\ldots,M,
  \label{eqn:stokeslet_rotlet}
\end{align}
where  $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
$\ell^{th}$ body, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then,
any solution of the Stokes equations with a Dirichlet boundary condition
$\ff$ can be written in terms of the completed double-layer potential
\begin{align}
  \label{eqn:completed_DLP}
  \uu(\xx) = \DD[\eeta](\xx) + 
    \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
    \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{subequations}
\label{eqn:completed_BIE}
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DD[\eeta](\xx) + 
      \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
      \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx) + \NN_0[\eeta](\xx),
      \quad \xx \in \bd\Omega, 
      \label{eqn:DLP}\\
  \llambda_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \eeta(\yy) \, ds_\yy,
  \quad \ell=1,\ldots,M,
  \label{eqn:stokeslet} \\
  \xi_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \yy^\perp \cdot \eeta(\yy)
  \, ds_\yy, \quad \ell=1,\ldots,M.
  \label{eqn:rotlet}
\end{align}
\end{subequations}
Here,
\begin{align*}
  \NN_0[\eeta](\xx) = \int_{\Gamma} 
    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy
\end{align*}
removes the rank one null space that results from the compatibility
constraint associated with the flux-free requirement of $\ff$.
